% resume.tex
% vim:set ft=tex spell:

\documentclass[12pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.8in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{hyperref}
\usepackage{fontawesome}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}
\raggedbottom
\raggedright
\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=black,
}

\newcommand{\area}[2]{\emph{#1:}   #2}
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }}
\newcommand{\contact}[3]{
\vspace*{-8pt}
\begin{center}
{\LARGE \scshape {#1}}\\
#2 \lineunder 
#3
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep 0pt}}{\vspace*{4pt}\end{list}}

\newcommand{\subemployment}[3]{
	\headerrow
		{\hspace{8pt}\textbf{\emph{#1}}}
		{\emph{#2}}
	\vspace*{-15pt}
	\begin{itemize*}
		\item #3
	\end{itemize*}
}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

\newcommand{\education}[5]{
	\headerrow
		{\textbf{#1}}
		{\textbf{#2}}
	\\
	\headerrow
		{\emph{#3}}
		{\emph{#4}}
    #5
}

\newcommand{\employment}[5]{
	\headerrow
		{\textbf{#1}}
		{\textbf{#2}}
	\\
	\headerrow
		{\emph{#3}}
		{\emph{#4}}
	\begin{itemize*}
		\item #5
	\end{itemize*}
}

\newcommand{\employmentNoList}[5]{
	\headerrow
		{\textbf{#1}}
		{\textbf{#2}}
	\\
	\headerrow
		{\emph{#3}}
		{\emph{#4}}
	#5
}


% and the actual content starts here
\begin{document}
\small
\smallskip
\vspace*{-30pt}

\contact{Jason Bowman}
{San Francisco, CA}
{\faPhone \hspace{0.1em} (650) 445-9552 \hspace{0.1em} \faEnvelope \hspace{0.1em}
  \href{mailto:sinistar@gmail.com}{jason@json64.dev} \hspace{0.1em} \faGithub \hspace{0.1em} \href{https://www.github.com/sini}{sini} \hspace{0.1em} \hspace{0.1em} \faLinkedin \hspace{0.1em}
  \href{https://linkedin.com/in/sinistar}{sinistar}}

\vspace*{3pt}

% \header{Overview}
% \begin{overview}\setlength{\parindent}{15pt}
% Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
% \end{overview}
% \\
% \vspace*{3pt}
\header{Education}
\education{The University of Alabama}{Tuscaloosa, AL}{Masters of Science in
  Computer Science (MSc), College of Engineering}{Dec 2012}{
	\begin{itemize*}
		\item \area{Select
    coursework}{Security $\cdot$ Cryptography $\cdot$ Advanced Computer
    Networking $\cdot$ Compilers}
    % $\cdot$ Cloud Computing
	\end{itemize*}
	\headerrow{\emph{Bachelors of Science in Computer Science (BSc), College of
      Engineering}}{\emph{May 2011}}
	\begin{itemize*}
  \item \emph{Minor in Mathematics}
	\end{itemize*}
}

% \education{The University of Alabama}{Tuscaloosa, AL}{Bachelors of Science in Computer Science (BSc), College of Engineering}{May 2011}{Minor in Mathematics}

\vspace*{3pt}

\header{Skills}
\vspace*{-5pt}
\begin{itemize*}
\item Proficient in application development with Scala, Java, Python, Go, C/\CPP, Ruby, and UNIX shell scripting. 
\item Experience with distributed systems, streaming data processing, security auditing, elastic
  computing, API design, performance optimization, graceful error detection and
  fault recovery, and full stack application development.
\item Experience architecting, scaling, and optimizing high volume QPS applications in hyper-growth environments.
\item Experience building developer experience tools, continuous integration
  systems, and production infrastructure services.
\item Over 25 years experience with GNU/Linux and other UNIX platforms.
\item Technical project management and organizational leadership experience.
\end{itemize*}
\vspace*{3pt}

\header{Related Experience}
\employment{Highnote}{San Francisco, CA}{Senior Software Engineer}{Aug 2022 - Sep 2023}{
Infrastructure engineering for B2B card issuer fintech, focusing on data systems and large-scale platform migrations.
\item \area{Spanner Replication System}{Implemented transaction log replay and mirroring system using Google Dataflow to enable cross-region Spanner cluster replication, ensuring 99.99\% uptime for payment processing systems.}
\item \area{Platform Modernization}{Led mono-repo wide framework upgrades affecting 50+ microservices. Built custom AST parsing tools and automated migration utilities, reducing manual effort by 80\% and eliminating version skew across services.}
\item Built data pipeline infrastructure for real-time payment analytics and fraud detection, processing millions of transactions daily with sub-100ms latency requirements.
}

\employment{Unity Technologies}{San Francisco, CA}{Senior Software Engineer / Tech Lead}{Jul 2018 - Aug 2022}{
Led engineering teams and architected large-scale data platform infrastructure serving Unity's analytics and ML workloads.
\item \area{Data Platform Team Lead}{Led team of 6 engineers in complete re-architecture of analytics ingestion pipeline during AWS to GCP migration. Implemented BigQuery-based data lake processing 1M events/sec (10B daily) using Google Dataflow/Apache Beam.}
\item \area{GDPR Compliance \& Data Governance}{Designed and implemented end-to-end data encryption and cryptographic protections. Built automated schema inference tools to identify PII in unstructured data, enabling data owners to annotate and classify sensitive information.}
\item \area{ML-Agents Cloud Platform}{Architected cloud-native reinforcement learning platform on GKE, providing framework for managing distributed training experiments and Unity simulation builds. Enabled researchers to scale RL training across hundreds of nodes.}
\item \area{Unity Simulation \& Robotics}{Built remote tunneling infrastructure allowing secure access to Unity instances in shared cloud environments. Developed tooling to bridge on-premise robotics workflows with cloud-based simulation infrastructure.}
}


\employmentNoList{Uber Technologies, Inc}{San Francisco, CA}{Software Engineer}{Jan 2015 - Jul 2018}{
  \\
 \subemployment{Marketplace Engineering // Fares}{Nov 2016 - Dec 2019}{
 Led development of end-user facing product features spanning back-end services and mobile applications.
\item \area{[Tech Lead] Pricing Integrity Engine}{Built real-time and batch data validation platform for fare data with configurable business rules, analytics, and automatic remediation.}
\item \area{Fares Platform}{Developed next-generation fare calculation platform for all Uber products using descriptive DSL, integrating tolls, maps, surge, and subscription data.}
\item \area{Promotions Platform}{Built auditing and remediation tools for post-transaction analysis of user promotions across real-time systems.}
}

\subemployment
{Site Reliability Engineering // Streaming SRE}{Dec 2015 - Oct 2016}{
Senior engineer on newly formed Streaming SRE team. Led team building and mentored junior engineers while scaling Kafka infrastructure to thousands of brokers processing >500GiB/s across multiple regions.
\item \area{Kafka Infrastructure Projects}{Built intelligent partition redistribution tool achieving optimal load balancing within 0.0001\% standard deviation and enabling self-healing of broker failures. Implemented performance optimizations increasing throughput >500\% and reducing p99 latencies by 5000\%, saving hundreds of millions in projected operational and hardware costs.}
}

\subemployment
  {Platform Engineering // Data Engineering Embed}
  {Jan 2015 - Dec 2015}{
Supported Data organization representing 30\% of Uber's hardware footprint. Built automation for provisioning, replication, ETL, and cluster management across Vertica, Hadoop, Redis, and MemSQL.
\item Designed data security architecture and compliance tools for global expansion into China, India, and Russia.
\item \area{[Tech Lead] uServer}{Built self-service hardware provisioning platform adopted company-wide, provisioning hundreds of thousands of bare-metal hosts across our datacenters.}
}
}

% \header{Related Experience - Continued}
\employment{Rocket Lawyer}{San Francisco, CA}{Senior Systems Engineer (original
  title: Systems Engineer)}{Jan 2013 - Jan 2015}{
Designed service infrastructure and provided 24/7 on-call support for a high
volume e-commerce site in the legal services sector, running primarily on the
JVM and a legacy .NET platform. Improved site reliability from 99\% uptime to 99.99\%
and reduced p99 latencies from 2000ms to 150ms.
\item Performance analysis and optimization of application services and supporting infrastructure services.
\item Extended application code to expose internal application
  state, key performance metrics, enrich logging, and reduce overall latencies.
  Implemented dynamic service discovery and reconfiguration via ZooKeeper.
\item Built tooling for continuous integration, dynamic configuration
  management, deployment management, monitoring, and automated incident
  detection and remediation.
}

\employment{nine.is}{Tuscaloosa, AL}{Software Engineer / Web Developer}{Jan 2012 - Dec 2012}{
Full-stack development and team leadership for design company transitioning to in-house software development. Built applications using PHP, JavaScript, and Ruby on Rails.
%Development and maintenance of multiple existing and new projects for this small design company in a several languages and frameworks including PHP, JavaScript, and Ruby on Rails.
%\item Built and led a team of junior engineers to transition nine.is from an
%  outsource contract based operation to doing their own in-house software development.
}

\employment{The University of Alabama}{Tuscaloosa, AL}{Graduate Research Assistant}{Jan 2010 - Dec 2012}{
Research on network optimization and security for next-generation internet infrastructure. Developed custom TCP variants and performed security analysis for GENI experimental network testbed.
%Research on proactive and adaptive techniques for cross-layer network
%reconfiguration in an effort to optimize performance when a network
%is under load or attack by hostile actors. Project details subject to export control restrictions.
%\item Worked on the Linux networking stack, defining a custom TCP variant
%  routing protocol, and physical device driver modification for fine parameter tuning and performance analysis.
%\item Security analysis and architecture design for GENI, a global network
%  research experimentation test-bed for developing new internet routing technologies.
%\item Application development and implementation of an autonomous cross-layer networking scheme utilizing C, Python, and Java, and an adaptive video streaming client application utilizing Java and gstreamer.
%\item Design and implementation of a universal description language for robots and their capabilities to further development of a deterministic universal device driver for most robots.
%\item Research on automated auditing, analysis, and penetration testing of virtual machine images for use in cloud computing - an extension of my work on GENI.
%\item Experimentation with Delay Tolerant Networks, optimizing cost in low connectivity environments with throwboxes.
%\item Opportunistic Network Environment (ONE) Simulator - Extended the simulation environment to support simple throwbox placement and management with geographical mapping tools. Implemented, modified, and experimented with multiple DTN protocols.
}

\employment{Brewer Porch Children's Center}{Tuscaloosa, AL}{Unix Systems Administrator}{Aug 2004 - May 2006}{
Systems administration for healthcare organization. Managed Linux/Solaris infrastructure and ensured HIPAA compliance for patient data systems.
%Managed numerous services including samba, mail, file, billing, print, web, and applications servers running on Linux, Solaris, and Microsoft Server systems.
%\item Maintained strict networking and client security policies in compliance with HIPAA regulations.
%\item Developed custom applications for internal organization management and patient document processing.
}

\vspace*{3pt}

\header{Publications}
\vspace*{-5pt}
\begin{itemize*}
\item Dawei Li, Jason Bowman, Xiaoyan Hong "Evaluation of Security Vulnerabilities by Using ProtoGENI as a Launchpad", IEEE Globecom 2011, Houston, USA, Dec. 2011.
\item M. Anderson, P. Kilgo, and J. Bowman. "RDIS: Generalizing domain concepts to specify device to framework mappings." In International Conference on Robotics and Automation, 2012. http://ua-robotics.net/index.php?title=RDIS
\end{itemize*}

\vspace*{3pt}

\header{Outreach and Community Involvement}
\vspace*{-5pt}
\begin{itemize*}
\item Mentor for Hackbright Academy, a 12 week intensive coding bootcamp focused
  on empowering women aiming to pursue a career in the software engineering field.
\item Mentor for dev/Mission, a non-profit program targeting low income youth
  from 16-24 to expose them to potential careers in technology.
\item Organized and ran an introduction to Scala and Functional Programming
  course based on Martin Odersky\'s course and book. Resources available on
  my personal github. 
\item Served as president from 2010 - 2012 of the Association for Computing
  Machinery student chapter at The University of Alabama.
\item Organized a mentoring/tutoring program for freshman and sophomore computer
  science students in an effort to improve program retention and graduation
  rates. Still going to this day, and graduation rates of freshman classes are
  up from 5\% to nearly 50\%.
\end{itemize*}

\vspace*{3pt}

\header{Interests}
\vspace*{-5pt}
\begin{itemize*}
\item \textbf{Professional:} GNU/Linux$\cdot$ Distributed Systems $\cdot$ Open Source $\cdot$
  System Architecture $\cdot$ Operating Systems $\cdot$ Functional Programming
  $\cdot$ Stream Processing $\cdot$ Virtualization $\cdot$
  Generative Programming $\cdot$ Language Development
\item \textbf{Personal:} Privacy $\cdot$ Reverse Engineering $\cdot$ Game
  Development \& Theory $\cdot$ Music Production $\cdot$ Electrical Engineering
  $\cdot$ Embedded Systems $\cdot$ Fabrication and DIY $\cdot$ Robotics $\cdot$ Mechanical
  Keyboards $\cdot$ CAD Design $\cdot$ Rock Climbing $\cdot$ Emacs 
\end{itemize*}
\vspace*{8pt}

\end{document}
